The SMT Competition 2015--2018

### 2019-08-22 2018/report/SMT-COMP.tex
Remove \rem and \todo commands
Shorter discussion of benchmark selection (no families mentioned)
Explanation of families in Section 7

\newcommand{\rem}[1]{\textcolor{red}{[#1]}}
\newcommand{\todo}[1]{\rem{TODO #1}}

@@

\paragraph{Benchmark Selection.}
SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers''~\cite{CSW15}. Together with the increased
computational resources available to the competition since its move to
StarExec, this finding prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible benchmarks.
This change had an unintended side effect: the pseudo-random selection
process had been purposely constrained to choose benchmarks from
different benchmark families (that is, groups of benchmarks with
similar characteristics).

@@

Until 2015, the competition used these raw scores for all tracks to determine
the division score of a solver as the sum of the scores of all benchmarks in
that division.
Fewer errors in a division takes precedence over more correct solutions
(resp.~reduction), which takes precedence over less wall-clock time taken,
which takes precedence over less CPU time taken.
However, since there are vast differences in size between benchmark families in
the SMT Library, the competition since~2016 uses a scoring method that assigns
a weight to each benchmark in the \maintrack and \ucoretrack in order to
de-emphasize large benchmark families~\cite{rules16,rules17,rules18}.
For application track divisions, division scores were still based on raw scores
only, since application track benchmarks may be partially solved. Defining a
useful sequential score for the application track would require information not
provided by the raw score, e.g., detailed timing information for each result.

>>>>

@@

\paragraph{Benchmark Selection.}
SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers''~\cite{CSW15}. Together with the increased
computational resources available to the competition since its move to
StarExec, this finding prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible benchmarks.

@@

Until 2015, the competition used these raw scores for all tracks to
determine the division score of a solver as the sum of the scores of
all benchmarks in that division.  Fewer errors in a division takes
precedence over more correct solutions (resp.~reduction), which takes
precedence over less wall-clock time taken, which takes precedence
over less CPU time taken.  However, since there are vast differences
in size between benchmark families (i.e., groups of benchmarks with
similar characteristics) in the SMT Library, the competition
since~2016 uses a scoring method that assigns a weight to each
benchmark in the \maintrack and \ucoretrack in order to de-emphasize
large benchmark families~\cite{rules16,rules17,rules18}.  For
application track divisions, division scores were still based on raw
scores only, since application track benchmarks may be partially
solved.  Defining a useful sequential score for the application track
would require information not provided by the raw score, e.g.,
detailed timing information for each result.
